\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
abstract and some intro hacking

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. It is now listed
as one of the ways that normal people use Tor.
We specifically examine its usability as a censorship circumvention tool,
an essential facet for adoption and use. We focus our analysis on the connection 
configuration interface of Tor Browser. We find that the Tor Browser 5.0.3. connection
configuration interface has a success rate of {\color {red} TODO}\% with the 
successful users having an average completion time of {\color {red} TODO} minutes. 
In this paper, we explore common challenges users faced during the configuration
process and redesign the interface to improve success rate to {\color {red} TODO}\% 
and average completion time to {\color {red} TODO} minutes.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Although Tor~\cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

We believe that this is a great opportunity for user research. We have the opportunity to help users circumvent censorship more easily and provide them with extra security features, such as anonymity. Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users~\cite{dingledine2006anonymity}.

@@

Currently, {\color {red} TODO}\% of users fail and with the current interface for reasons {\color {red} TODO}, {\color {red} TODO}, and {\color {red} TODO}. Of those that do succeed, the average time to completion is {\color {red} TODO}. This can lead to a bad user experience, users quitting Tor, or causing high-risk users to make mistakes. With the new design, only {\color {red} TODO}\% of users fail to configure successfully and the average time to completion is {\color {red} TODO}. Tor has already implemented some of these changes.

@@

An exploration of the problems with the existing Tor Browser 
configuration interface through user observation and interviews can be 
found in Section~{\color{red} TODO}. A heuristic evaluation of the existing interface and new interface is in Section~{\color{red} TODO}. We empirically show 
that the redesigned interface improves completion rate, reduces time to completion, 
and provides a safe path for at-risk users in Section~{\color{red} TODO}.

>>>>

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. We conducted a series of 
experiments to improve the Tor launcher configuration interface, which configures network components
that circumvent censorship. A 16-participant experiment and interview
identifies common user struggles while circumventing censorship.
We use as feedback to redesign the configuration interface.
We test the impact of our
changes on 124 participants to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Although Tor~\cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's anonymizing functionality also circumvented censorship. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor's network of unlisted relays and various methods of obfuscation making it a viable censorship circumvention tool even in the face of nation-state level adversaries.

To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool. We believe that this is a great opportunity for user research, both for investigating a case study of how users circumvent censorship, but also to help Tor users circumvent censorship more easily and provide them with extra security features, such as anonymity. Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users~\cite{dingledine2006anonymity}.

@@

@@
